\sysfull

### 2019-10-02 paper/TOSN/relatedwork.tex
correction of bin file (inlcuding removal of duplicate reference to Wisent

\paragraph{Intermittently-powered Devices.}
There is a large body of research on energy-harvesting and ambient-powered embedded devices summarized by~\cite{prasad_comst_2014,sample_procieee_2013,huang:commag:2015,visser_procieee_2013,kamalinejad_commag_2015,ku_cst_2016}. For instance, a new wave of embedded systems powered by radio waves is emerging~\cite{patel_pervasive_2017,rf_powered_computing_gollakota_2014,wisp5,moo,zhao_rfid_2015,holleman_biocas_2008,thomas_jbcs_2012,naderiparizi_rfid_2015,rodriguez_tbcs_2015,liu_sigcomm_2013,kicksat,nadeau_naturebio_2017}. The emergence of such hardware platforms
has led to the development of instrumentation, debugging, and prototyping tools for such systems
~\cite{hester_sensys_2014,hester_sensys_2015,edb,capybara,stork,wisent,flicker}.

>>>>

\paragraph{Intermittently-powered Devices.}
There is a large body of research on energy-harvesting and ambient-powered embedded devices summarized by~\cite{prasad_comst_2014,sample_procieee_2013,huang:commag:2015,visser_procieee_2013,kamalinejad_commag_2015,ku_cst_2016}. For instance, a new wave of embedded systems powered by radio waves is emerging~\cite{patel_pervasive_2017,rf_powered_computing_gollakota_2014,wisp5,moo,zhao_rfid_2015,holleman_biocas_2008,thomas_jbcs_2012,naderiparizi_rfid_2015,rodriguez_tbcs_2015,liu_sigcomm_2013,kicksat,nadeau_naturebio_2017}. The emergence of such hardware platforms
has led to the development of instrumentation, debugging, and prototyping tools for such systems
~\cite{hester_sensys_2014,hester_sensys_2015,edb,capybara,stork,tan_infocom_2016,flicker}.
